\section{The Side Projects}

\subsection{Problematic}
\noindent
In parallel with the main Intern Management Platform project, VOID Digital Agency often encourages interns to contribute to smaller internal initiatives, known as \textbf{side projects}.  
These projects are crucial for addressing internal operational needs, testing new technologies, and improving the agency's digital ecosystem.  
During my internship, I was tasked with participating in the development and enhancement of several side projects that aimed to streamline internal workflows and enrich VOID's technical stack.

\medskip

\noindent
However, the side projects also posed certain challenges:
\begin{itemize}
\item Managing time between the main project and side initiatives without impacting overall deadlines.
\item Quickly adapting to different technical contexts (varying tech stacks, objectives, team sizes).
\item Maintaining a high level of code quality and documentation despite shorter timelines.
\end{itemize}

\subsection{Objectives}
\noindent
The objectives behind working on side projects were:

\begin{itemize}
\item \textbf{Skill Diversification:} Expose interns to different technologies and problem-solving contexts.
\item \textbf{Internal Efficiency:} Develop tools or features that optimize VOID's internal operations.
\item \textbf{Innovation:} Experiment with new technologies (e.g., emerging frameworks, DevOps techniques) without risking main production systems.
\item \textbf{Collaboration:} Foster collaboration across different teams and encourage knowledge sharing.
\item \textbf{Professionalism:} Apply the same development standards (agile, CI/CD) used in main projects, even for small-scale tools.
\end{itemize}

\subsection{Proposed Solution}
\noindent
Throughout my internship, I contributed to two major side projects that played a significant role in enhancing VOID's internal infrastructure and its client service capabilities:

\begin{itemize}
\item \textbf{Project Migration to Internal Infrastructure:}  
As part of VOID's initiative to internalize hosting services, I participated in the migration of the official website of \href{https://www.cmi.co.ma/}{CMI (Centre Monétique Interbancaire)} from the \textit{sooninprod} external cloud server to the newly acquired \textit{leserveurdetest} (an Apple Mac Studio server).  
This task involved:
\begin{itemize}
\item Building a custom Docker image to support an older PHP version required by the legacy project.
\item Migrating and reconfiguring the database to match the new environment specifications.
\item Ensuring compatibility between the existing codebase and the new server settings.
\item Performing comprehensive testing post-migration to guarantee full operational stability.
\end{itemize}

\item \textbf{Custom Module Development for VOID Factory (Vactory):}  
VOID Digital Agency leverages its proprietary technical foundation called the \textbf{VOID Factory}, a product of over a decade of digital experience and innovation.  
The VOID Factory, maintained and evolved by the internal Core Team, is based on robust open-source technologies such as Drupal, Symfony, and React, and follows agile development practices to stay aligned with modern digital standards.  
As part of the continuous evolution of Vactory, I was tasked with:
\begin{itemize}
\item Developing custom Drupal modules needed for client-specific requirements, including an \textbf{Appointment Booking Module}.
\item Adhering to the Factory's high standards for modularity, scalability, and integration with decoupled architectures.
\item Following best practices in automated testing and DevOps processes to ensure production-quality deliverables.
\end{itemize}
\end{itemize}

\medskip

\noindent
These side projects allowed me to deepen my technical skills across DevOps, backend development, and modular architecture design, while also contributing tangible value to VOID's internal operations and client offerings.

