% frontmatter/acknowledgement.tex
\chapter*{Acknowledgement}
\thispagestyle{empty}
\addcontentsline{toc}{chapter}{Acknowledgement}

\indent As I reflect on this transformative journey, I am filled with profound gratitude for the countless individuals who have contributed to the success of this internship and the completion of this report. Their guidance, support, and wisdom have been instrumental in shaping not just this project, but my professional growth.

\bigskip

\indent My deepest appreciation goes to \textbf{Professor Mustapha Hain} of ENSAM Casablanca, whose academic mentorship has been nothing short of transformative. His insightful guidance, rigorous feedback, and unwavering encouragement have not only enhanced the quality of this work but have also profoundly influenced my approach to problem-solving and research.

\bigskip

\indent I am equally indebted to \textbf{Mr.~Hamza Bahlaouane} at VOID Digital Agency, whose visionary leadership and technical expertise have been pivotal to this project's success. His trust in my capabilities, willingness to share knowledge, and commitment to fostering innovation have created an environment where learning and growth flourished.

\bigskip

\indent The VOID team has been an exceptional source of inspiration and support. I am particularly grateful to:
\begin{itemize}
  \item \textbf{Mr. Yahya Chahine} (DevOps Engineer) for his invaluable technical guidance and patient mentorship
  \item \textbf{Mr. Mjid} (Project Director) for his strategic vision and leadership
  \item \textbf{Mr. Khalid} (Technical Lead) for his technical expertise and mentorship
  \item \textbf{Mr. Salah} (Full Stack Developer) for his collaborative spirit and technical insights
  \item \textbf{Mr. Karim} and \textbf{Mr. Mounssif} (Frontend Developers) for their teamwork and support
\end{itemize}

\bigskip

\indent The foundation of this practical work rests upon the solid theoretical knowledge imparted by the distinguished university at ENSAM, whose dedication to excellence in teaching has been fundamental to my academic journey. To my family and friends, whose unwavering support and encouragement have been my constant source of strength — your belief in me has made this achievement possible and this work is as much yours as it is mine.

\clearpage
