\section{Specification Document}
\noindent
This specification document outlines the essential requirements and criteria for the Intern Management Platform, as defined through stakeholder collaboration and technical analysis. The document is structured to provide a clear reference for both development and evaluation.

\subsection{Functional Requirements}
\begin{itemize}
    \item \textbf{Main Website:} Provide a public-facing portal that presents VOID's internship program, company values, and available opportunities, with clear calls-to-action redirecting candidates to the application process.
    \item \textbf{Candidate Space:} Enable candidates to create accounts, submit applications, upload required documents (CV, cover letter, etc.), and track their application status in real time.
    \item \textbf{Automated Technical Testing:} Integrate an automated technical test system that assigns, grades, and filters candidates based on their results, ensuring only competent applicants proceed.
    \item \textbf{Challenge Submission and Review:} Allow selected candidates to receive and submit coding or project challenges, with manual review and feedback by supervisors.
    \item \textbf{Video Interview Integration:} Facilitate asynchronous or scheduled video interview submissions, enabling supervisors to assess communication and motivation.
    \item \textbf{Selective Progression:} Implement a workflow where only candidates who pass all evaluation stages (technical test, challenge, video) are accepted as pre-hire interns (pre-embauche).
    \item \textbf{Training Space:} Provide a dedicated area for accepted interns to access learning resources, follow personalized training paths, complete quizzes, and track their progress.
    \item \textbf{Supervisor and Admin Tools:} Equip supervisors and administrators with dashboards for monitoring candidate progress, managing challenges, reviewing submissions, and generating evaluation reports and certificates.
    \item \textbf{Communication and Notification:} Ensure timely, automated notifications and messaging between candidates, supervisors, and HR throughout all stages.
    \item \textbf{Data Security and Privacy:} Enforce role-based access, secure authentication, and compliance with data protection standards for all user data and documents.
\end{itemize}

\subsection{Non-Functional Requirements}
\begin{itemize}
    \item \textbf{Scalability:} The system must support at least 50 concurrent users and handle 100+ intern records simultaneously.
    \item \textbf{Security:} Sensitive data must be protected through encryption, secure authentication (OAuth 2.0 or equivalent), and audit logging.
    \item \textbf{Performance:} Application response times should not exceed 2 seconds for standard operations under normal load.
    \item \textbf{Reliability:} The platform should maintain 99.5\% uptime, with automated backups and disaster recovery procedures in place.
    % \item \textbf{Usability:} New users should be able to complete basic tasks with less than 30 minutes of training; usability testing should target at least 90\% satisfaction.
\end{itemize}

\subsection{Success Criteria}
\begin{itemize}
    \item The Main Website effectively communicates VOID's internship program and drives candidate engagement, as measured by application conversion rates.
    \item The Candidate Space enables at least 90\% of users to complete the application process without support, and provides real-time status updates at every stage.
    \item The technical test and challenge system successfully filters out unqualified candidates, with only those meeting predefined competency thresholds advancing to the next stage.
    \item Only candidates who pass all evaluation stages (technical test, challenge, video) are accepted as pre-hire interns, ensuring a high standard of competency and motivation.
    \item The Training Space is accessed by 100\% of accepted interns, with all interns completing assigned learning paths and quizzes.
    \item Supervisors and administrators report improved efficiency in candidate management, with a reduction in manual tracking and paperwork by at least 60\%.
    \item The platform maintains data integrity and security, with no reported breaches or unauthorized access incidents during the evaluation period.
\end{itemize}

\noindent
This specification document serves as a foundation for the design, implementation, and evaluation of the Intern Management Platform, ensuring that the solution meets both the immediate operational needs and the long-term strategic goals of VOID Digital Agency.
