\section{Study of the Existing System}
\noindent
Before the introduction of the Intern Management Platform, VOID Digital Agency \cite{void2025clients} managed internships using a patchwork of manual processes. Applications were tracked in Excel sheets, communications handled through scattered emails, and evaluations stored in separate documents. This fragmented approach created a number of persistent challenges for the organization.

\subsection{Operational Inefficiencies}
\begin{itemize}
    \item \textbf{Process Delays:} Manual data entry and document handling often led to delays of several days in processing applications.
    \item \textbf{Resource Intensive:} The HR team spent a significant amount of time on repetitive administrative tasks.
    \item \textbf{Error Prone:} A notable percentage of applications required manual correction due to data entry mistakes.
    \item \textbf{Inconsistent Documentation:} Evaluation forms and reports frequently lacked standardization, making it difficult to compare or aggregate results.
\end{itemize}

\subsection{Technical Limitations}
\begin{itemize}
    \item \textbf{Data Fragmentation:} Information was dispersed across multiple systems, making it hard to maintain a single source of truth.
    \item \textbf{Version Control Issues:} Multiple versions of documents circulated, leading to confusion and inconsistencies.
    \item \textbf{Limited Accessibility:} Accessing intern information remotely or collaboratively was often challenging.
    \item \textbf{Integration Challenges:} The lack of integration with existing HR and project management tools further complicated workflows.
\end{itemize}

\subsection{Impact on Stakeholders}
\begin{itemize}
    \item \textbf{Interns:} Experienced delays in feedback and had limited visibility into their own progress.
    \item \textbf{Supervisors:} Found it difficult to monitor and support multiple interns effectively.
    \item \textbf{HR Team:} Faced increased workloads and reduced overall efficiency.
    \item \textbf{Management:} Had limited insight into the overall performance and return on investment of the internship program.
\end{itemize}

\noindent
As the number of interns grew each quarter, these issues became more acute. Following the Software Development Life Cycle (SDLC) \cite{geeksforgeeks2025sdlc}, the situation underscored the urgent need for a centralized, automated, and scalable platform—one capable of supporting VOID's growth while ensuring data integrity, process efficiency, and a better experience for all stakeholders.