\chapter*{General Conclusion and Perspectives}
\addcontentsline{toc}{chapter}{General Conclusion and Perspectives}
\label{chap:conclusion}

The Intern Management Platform developed during this internship at VOID Digital Agency represents a significant transformation in how the company handles its recruitment process. What began as a challenge to manage over 600 annual applications through scattered emails and spreadsheets has evolved into a comprehensive, automated system that streamlines the entire recruitment workflow.

\medskip
\noindent
The technical architecture—combining Drupal 10 as a headless CMS with Next.js 13+ frontend—proved to be an excellent choice for this project. The decoupled approach provided the flexibility needed for complex content management while delivering the performance and user experience expected from modern web applications. The widget-based content management system emerged as a key innovation, allowing content editors to create dynamic layouts without technical intervention.

\medskip
\noindent
This internship experience provided far more than just technical skills development—it offered a comprehensive introduction to professional software development practices. Working on a real project with actual business impact taught invaluable lessons about software architecture, user experience design, and collaborative development methodologies. The challenges faced throughout the project—from debugging complex API integrations to optimizing Docker configurations—built confidence in tackling unfamiliar technologies and problem-solving under pressure.

\medskip
\noindent
Beyond the technical achievements, this experience demonstrated the critical importance of understanding user needs and designing solutions that genuinely improve workflows. The automated recruitment workflow reduced administrative overhead significantly while improving the candidate experience. The feedback sessions with candidates and staff provided valuable insights into user experience design principles that extend beyond technical implementation.

\medskip
\noindent
The platform's current success provides a strong foundation for future enhancements. The planned integration of VPS technology for development environments, enhanced administrative dashboards, and real-time collaboration features will further strengthen the platform's capabilities. From a personal perspective, this internship has clarified the type of developer I aspire to become: someone who writes code that solves real problems and makes people's work lives more efficient and enjoyable.

\medskip
\noindent
The technical skills acquired during this internship—ranging from modern frontend frameworks to backend architecture and DevOps practices—provide a competitive advantage in the job market. The experience of working with production systems and real business requirements demonstrates the ability to handle professional development challenges.

\medskip
\noindent
This internship at VOID Digital Agency has been a transformative experience that exceeded initial expectations. The Intern Management Platform stands as a testament to the power of modern web technologies when applied to real-world problems. Most importantly, this experience has reinforced the belief that software development is fundamentally about creating solutions that make people's lives better—a principle that will continue to drive professional growth and development.


