% sections/Introduction/introduction.tex
\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction}
\thispagestyle{plain}

\indent In today's digital landscape, building robust, scalable, and user-centric web platforms is crucial for staying competitive. Since 2005, \textbf{VOID Digital Agency} has established itself as a leader in UX and digital solutions, serving major clients across banking, telecom, healthcare, retail, and cultural sectors.

\bigskip

\indent During my final-year internship at \textbf{VOID}, I developed an \textbf{Intern Management Platform} using headless Drupal CMS and React/Next.js. This platform streamlines intern applications, onboarding, training, and evaluations. Additionally, I contributed to DevOps improvements, server migrations, and custom Vactory module development.

\bigskip

\indent This report is structured as follows:

\medskip

\textbf{Chapter 1: Context}
The first chapter presents the general context of the project, providing an overview of VOID Digital Agency, their services, and technical infrastructure.

\textbf{Chapter 2: Design}
This chapter details the analysis and design phase, covering requirements gathering, system architecture, and interface design for the Intern Management Platform.

\textbf{Chapter 3: Development}
The third chapter describes the implementation phase, focusing on frontend and backend development, along with CI/CD pipeline setup.

\textbf{Chapter 4: Results}
Chapter four evaluates the implemented solution and its impact on the internship management process.

\textbf{Chapter 5: Future}
The final chapter examines technical challenges encountered and proposes future improvements.

\bigskip

\indent Throughout this project, I applied agile Scrum methods and DevOps practices, including Bitbucket pipelines and Docker containerization. This report demonstrates how modern web architectures and automation contribute to building efficient, scalable digital platforms.

\clearpage
